---
title: "Gorilla.gorilla_Femur"
output: html_document
---

```{r, echo=FALSE,message=FALSE}
#Require packages:
library(plyr)
library(reshape2)
library(ggplot2)
library(ggthemes)


#Load and attach data ####
#Load source file with all Femur data
setwd("//Users/Carrie/Desktop/")
Femurdataframe <- read.table("Ape.Midshaft_Slice.Geometry.Ouput_femur.txt", header=T, sep="\t")

#Now we want only the gorilla gorilla gorilla data
#Pull out the specific specimens (by number-- in measurement list) which are gorilla gorilla gorilla

gorilla.1 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_AMNH_167337_Femur",]
gorilla.2 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_AMNH_167339_Femur",]
gorilla.3 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_AMNH_167335_Femur",]
gorilla.4 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_AMNH_201460_Femur",]
gorilla.5 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_AMNH_90289_Femur",]
gorilla.6 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_AMNH_167338_Femur",]
gorilla.7 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_AMNH_90290_Femur",]
gorilla.8 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_AMNH_81652_Femur",]
gorilla.9 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_AMNH_167340_Femur",]
gorilla.10 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_AMNH_54327_Femur",]
gorilla.11 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_AMNH_54356_Femur",]
gorilla.12 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_AMNH_54355_Femur",]
gorilla.13 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_MCZ_20043_Femur",]
gorilla.14 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_MCZ_26850_Femur",]
gorilla.15 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_MCZ_29048_Femur",]
gorilla.16 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_MCZ_23162_Femur",]
gorilla.17 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_MCZ_38326_Femur",]
gorilla.18 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_MCZ_37264_Femur",]
gorilla.19 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_MCZ_57482_Femur",]
gorilla.20 <- Femurdataframe[Femurdataframe[,2] == "Gorilla_MCZ_29049_Femur",]


gorilla.Femurdataframe <- rbind(gorilla.1, gorilla.2, gorilla.3, gorilla.4, gorilla.5, gorilla.6, gorilla.7, gorilla.8, gorilla.9, gorilla.10, gorilla.11, gorilla.12, gorilla.13, gorilla.14, gorilla.15, gorilla.16, gorilla.17, gorilla.18, gorilla.19, gorilla.20)

#Create rows for J and Imin/Imax
gorilla.Femurdataframe$J <- gorilla.Femurdataframe$Imin + gorilla.Femurdataframe$Imax
gorilla.Femurdataframe$ratio <- gorilla.Femurdataframe$Imax / gorilla.Femurdataframe$Imin


#dataframe must be attached for this function to work

data <- gorilla.Femurdataframe
attach(data)
```

######  Code to pull out CSA at 5% intervals and calculate percent differences. This is repeated verbatim for J and Imax/Imin.
```{r, message=FALSE}
midshaft.csa.function <- function(x)
{
  slicelength <- as.numeric(length(csa[which(label == x)]))
  slice.intervals <- as.integer(seq(1,slicelength, by=(slicelength*.05)))
  slice.intervals <- slice.intervals + min(slice[which(label == x)])
  slicelength <- slicelength + (min(slice[which(label == x)])-1)
  slice.bind <- cbind(seq((min(slice[which(label == x)])), slicelength), (csa[which(label == x)]))
  slice.bind <- rbind(matrix(nrow = (min(slice[which(label == x)])-1), ncol=2), slice.bind)
  slice.matrix <- as.matrix(slice.bind[slice.intervals, ])
  csa.levels <- data.frame(rbind(slice.matrix[,2]))
  csa.levels <- cbind(x, csa.levels)
  colnames(csa.levels) <- c("specimen", seq(0,95, by=5))
  perdiff <- rbind(((csa.levels[,2:21] - csa.levels[,12])/csa.levels[,12])*100)/length(unique(x))
  perdiff <- data.frame(cbind(x, perdiff))
  colnames(perdiff) <- c("specimen",seq(0,95, by=5))
  return(perdiff)
}

x <- as.vector(data$label)

result.csa = mdply(unique(x), midshaft.csa.function)


#Reshape into long format in order to plot 
result.csa.long <- melt(result.csa, variable.name="level", value.name="percent.difference")

result.csa.long <- rbind(result.csa.long[which(result.csa.long$level == 30),], 
                         result.csa.long[which(result.csa.long$level == 35),],
                         result.csa.long[which(result.csa.long$level == 40),],
                         result.csa.long[which(result.csa.long$level == 45),],
                         result.csa.long[which(result.csa.long$level == 50),],
                         result.csa.long[which(result.csa.long$level == 55),],
                         result.csa.long[which(result.csa.long$level == 60),],
                         result.csa.long[which(result.csa.long$level == 65),],
                         result.csa.long[which(result.csa.long$level == 70),])



#Now the same function, but with the raw data in order to perform the statistical tests (this is just repeating all steps up to, but not including calculating percentages) 
midshaft.raw.csa.function <- function(x)
{
  slicelength <- as.numeric(length(csa[which(label == x)]))
  slice.intervals <- as.integer(seq(1,slicelength, by=(slicelength*.05)))
  slice.intervals <- slice.intervals + min(slice[which(label == x)])
  slicelength <- slicelength + (min(slice[which(label == x)])-1)
  slice.bind <- cbind(seq((min(slice[which(label == x)])), slicelength), (csa[which(label == x)]))
  slice.bind <- rbind(matrix(nrow = (min(slice[which(label == x)])-1), ncol=2), slice.bind)
  slice.matrix <- as.matrix(slice.bind[slice.intervals, ])
  csa.levels <- data.frame(rbind(slice.matrix[,2]))
  csa.levels <- cbind(x, csa.levels)
  colnames(csa.levels) <- c("specimen", seq(0,95, by=5))
  return(csa.levels)
}


raw.csa.result = mdply(unique(x), midshaft.raw.csa.function)
raw.result.csa.long <- melt(raw.csa.result, variable.name="level", value.name="raw.value")


#inverse of previous result.csa.long to keep specimen names for the anova-- probably need to change for all 
raw.result.csa.long <- raw.result.csa.long[-c((which(raw.result.csa.long$level == 0)), (which(raw.result.csa.long$level == 5)),(which(raw.result.csa.long$level == 10)), (which(raw.result.csa.long$level == 15)),(which(raw.result.csa.long$level == 20)), (which(raw.result.csa.long$level == 25)),(which(raw.result.csa.long$level == 75)),(which(raw.result.csa.long$level == 80)),(which(raw.result.csa.long$level == 85)),(which(raw.result.csa.long$level == 90)),(which(raw.result.csa.long$level == 95))),]

```

######  Code for Significance testing of the raw, unadjusted CSA values. This is repeated verbatim for J and Imax/Imin.
```{r}
#Repeated measures ANOVA####
#Standard repeated measures anova (correcting for repeated measures from the same specimen)
m <- aov(terms(raw.result.csa.long$raw.value ~ raw.result.csa.long$level + (raw.result.csa.long$specimen)))
m <- TukeyHSD(m)
midshaft.aov <- c('50-30','50-35','50-40','50-45', '55-50', '60-50', '65-50','70-50')
csa.aov <- m$`raw.result.csa.long$level`[midshaft.aov,]



#Paired T-test of all levels against midshaft
csa.ttest <-as.data.frame(cbind( c(30,35,40,45,55,60, 65,70), c(t.test(raw.csa.result$'50', raw.csa.result$'30', paired=T)$p.value,
                                                                t.test(raw.csa.result$'50', raw.csa.result$'35', paired=T)$p.value,
                                                                t.test(raw.csa.result$'50', raw.csa.result$'40', paired=T)$p.value,
                                                                t.test(raw.csa.result$'50', raw.csa.result$'45', paired=T)$p.value,
                                                                t.test(raw.csa.result$'50', raw.csa.result$'55', paired=T)$p.value,
                                                                t.test(raw.csa.result$'50', raw.csa.result$'60', paired=T)$p.value,
                                                                t.test(raw.csa.result$'50', raw.csa.result$'65', paired=T)$p.value,
                                                                t.test(raw.csa.result$'50', raw.csa.result$'70', paired=T)$p.value)))
colnames(csa.ttest) <- c("level", "p-value")
#Bonferroni Correction to these p-values
csa.ttest[,2] <- p.adjust(csa.ttest[,2], method = "bonferroni", n = length(csa.ttest[,2]))

#Compare Results of ANOVA and T-test:
csa.pvalues <- cbind(csa.aov[,-c(1:3)], csa.ttest[,2])
colnames(csa.pvalues) <- c("R.M. ANOVA", "Paired T-Test")

```

####  P-values of Repeated measures Anova and Paired T-tests: CSA
```{r}
csa.pvalues
```

```{r, echo=FALSE,message=FALSE, results='hide'}
#J Analysis ####
# Function to pull out J at intervals and compile into dataframe 


midshaft.J.function <- function(x)
{
  slicelength <- as.numeric(length(J[which(label == x)]))
  slice.intervals <- as.integer(seq(1,slicelength, by=(slicelength*.05)))
  slice.intervals <- slice.intervals + min(slice[which(label == x)])
  slicelength <- slicelength + (min(slice[which(label == x)])-1)
  slice.bind <- cbind(seq((min(slice[which(label == x)])), slicelength), (J[which(label == x)]))
  slice.bind <- rbind(matrix(nrow = (min(slice[which(label == x)])-1), ncol=2), slice.bind)
  slice.matrix <- as.matrix(slice.bind[slice.intervals, ])
  J.levels <- data.frame(rbind(slice.matrix[,2]))
  J.levels <- cbind(x, J.levels)
  colnames(J.levels) <- c("specimen", seq(0,95, by=5))
  perdiff <- rbind(((J.levels[,2:21] - J.levels[,12])/J.levels[,12])*100)/length(unique(x))
  perdiff <- data.frame(cbind(x, perdiff))
  colnames(perdiff) <- c("specimen",seq(0,95, by=5))
  return(perdiff)
}

x <- as.vector(data$label)

result.J = mdply(unique(x), midshaft.J.function)


#Reshape into long format in order to plot 
result.J.long <- melt(result.J, variable.name="level", value.name="percent.difference")

result.J.long <- rbind(result.J.long[which(result.J.long$level == 30),], 
                       result.J.long[which(result.J.long$level == 35),],
                       result.J.long[which(result.J.long$level == 40),],
                       result.J.long[which(result.J.long$level == 45),],
                       result.J.long[which(result.J.long$level == 50),],
                       result.J.long[which(result.J.long$level == 55),],
                       result.J.long[which(result.J.long$level == 60),],
                       result.J.long[which(result.J.long$level == 65),],
                       result.J.long[which(result.J.long$level == 70),])



#Now the same function, but with the raw data in order to perform the statistical tests (this is just repeating all steps up to, but not including calculating percentages) 
midshaft.raw.J.function <- function(x)
{
  slicelength <- as.numeric(length(J[which(label == x)]))
  slice.intervals <- as.integer(seq(1,slicelength, by=(slicelength*.05)))
  slice.intervals <- slice.intervals + min(slice[which(label == x)])
  slicelength <- slicelength + (min(slice[which(label == x)])-1)
  slice.bind <- cbind(seq((min(slice[which(label == x)])), slicelength), (J[which(label == x)]))
  slice.bind <- rbind(matrix(nrow = (min(slice[which(label == x)])-1), ncol=2), slice.bind)
  slice.matrix <- as.matrix(slice.bind[slice.intervals, ])
  J.levels <- data.frame(rbind(slice.matrix[,2]))
  J.levels <- cbind(x, J.levels)
  colnames(J.levels) <- c("specimen", seq(0,95, by=5))
  return(J.levels)
}


raw.J.result = mdply(unique(x), midshaft.raw.J.function)
raw.result.J.long <- melt(raw.J.result, variable.name="level", value.name="raw.value")


#inverse of previous result.J.long to keep specimen names for the anova-- probably need to change for all 
raw.result.J.long <- raw.result.J.long[-c((which(raw.result.J.long$level == 0)), (which(raw.result.J.long$level == 5)),(which(raw.result.J.long$level == 10)), (which(raw.result.J.long$level == 15)),(which(raw.result.J.long$level == 20)), (which(raw.result.J.long$level == 25)),(which(raw.result.J.long$level == 75)),(which(raw.result.J.long$level == 80)),(which(raw.result.J.long$level == 85)),(which(raw.result.J.long$level == 90)),(which(raw.result.J.long$level == 95))),]


#Repeated measures ANOVA####
#Standard repeated measures anova (correcting for repeated measures from the same specimen)
m <- aov(terms(raw.result.J.long$raw.value ~ raw.result.J.long$level + (raw.result.J.long$specimen)))
m <- TukeyHSD(m)
midshaft.aov <- c('50-30','50-35','50-40','50-45', '55-50', '60-50', '65-50','70-50')
J.aov <- m$`raw.result.J.long$level`[midshaft.aov,]



#Paired T-test of all levels against midshaft
J.ttest <-as.data.frame(cbind( c(30,35,40,45,55,60, 65,70), c(t.test(raw.J.result$'50', raw.J.result$'30', paired=T)$p.value,
                                                              t.test(raw.J.result$'50', raw.J.result$'35', paired=T)$p.value,
                                                              t.test(raw.J.result$'50', raw.J.result$'40', paired=T)$p.value,
                                                              t.test(raw.J.result$'50', raw.J.result$'45', paired=T)$p.value,
                                                              t.test(raw.J.result$'50', raw.J.result$'55', paired=T)$p.value,
                                                              t.test(raw.J.result$'50', raw.J.result$'60', paired=T)$p.value,
                                                              t.test(raw.J.result$'50', raw.J.result$'65', paired=T)$p.value,
                                                              t.test(raw.J.result$'50', raw.J.result$'70', paired=T)$p.value)))
colnames(J.ttest) <- c("level", "p-value")
#Bonferroni Correction to these p-values
J.ttest[,2] <- p.adjust(J.ttest[,2], method = "bonferroni", n = length(J.ttest[,2]))

#Compare Results of ANOVA and T-test:
J.pvalues <- cbind(J.aov[,-c(1:3)], J.ttest[,2])
colnames(J.pvalues) <- c("R.M. ANOVA", "Paired T-Test")
J.pvalues


#And the same significance tests on the logged values####
m <- aov(terms(log(raw.result.J.long$raw.value) ~ raw.result.J.long$level + (raw.result.J.long$specimen)))
m <- TukeyHSD(m)
midshaft.aov <- c('50-30','50-35','50-40','50-45', '55-50', '60-50', '65-50','70-50')
log.J.aov <- m$`raw.result.J.long$level`[midshaft.aov,]

#Paired T-test of all levels against midshaft
log.J.ttest <-as.data.frame(cbind( c(30,35,40,45,55,60, 65,70), c(t.test(log(log(raw.J.result$'50')), log(raw.J.result$'30'), paired=T)$p.value,
                                                                  t.test(log(raw.J.result$'50'), log(raw.J.result$'35'), paired=T)$p.value,
                                                                  t.test(log(raw.J.result$'50'), log(raw.J.result$'40'), paired=T)$p.value,
                                                                  t.test(log(raw.J.result$'50'), log(raw.J.result$'45'), paired=T)$p.value,
                                                                  t.test(log(raw.J.result$'50'), log(raw.J.result$'55'), paired=T)$p.value,
                                                                  t.test(log(raw.J.result$'50'), log(raw.J.result$'60'), paired=T)$p.value,
                                                                  t.test(log(raw.J.result$'50'), log(raw.J.result$'65'), paired=T)$p.value,
                                                                  t.test(log(raw.J.result$'50'), log(raw.J.result$'70'), paired=T)$p.value)))
colnames(log.J.ttest) <- c("level", "p-value")
#Bonferroni Correction to these p-values
log.J.ttest[,2] <- p.adjust(J.ttest[,2], method = "bonferroni", n = length(J.ttest[,2]))


#Compare Results of logged ANOVA and T-test:
log.J.pvalues <- cbind(log.J.aov[,-c(1:3)], log.J.ttest[,2])
colnames(log.J.pvalues) <- c("R.M. ANOVA", "Paired T-Test")
log.J.pvalues


###############################################################################################################################################

#Imax/Imin Analysis ####
# Function to pull out ratio at intervals and compile into dataframe 

midshaft.ratio.function <- function(x)
{
  slicelength <- as.numeric(length(ratio[which(label == x)]))
  slice.intervals <- as.integer(seq(1,slicelength, by=(slicelength*.05)))
  slice.intervals <- slice.intervals + min(slice[which(label == x)])
  slicelength <- slicelength + (min(slice[which(label == x)])-1)
  slice.bind <- cbind(seq((min(slice[which(label == x)])), slicelength), (ratio[which(label == x)]))
  slice.bind <- rbind(matrix(nrow = (min(slice[which(label == x)])-1), ncol=2), slice.bind)
  slice.matrix <- as.matrix(slice.bind[slice.intervals, ])
  ratio.levels <- data.frame(rbind(slice.matrix[,2]))
  ratio.levels <- cbind(x, ratio.levels)
  colnames(ratio.levels) <- c("specimen", seq(0,95, by=5))
  perdiff <- rbind(((ratio.levels[,2:21] - ratio.levels[,12])/ratio.levels[,12])*100)/length(unique(x))
  perdiff <- data.frame(cbind(x, perdiff))
  colnames(perdiff) <- c("specimen",seq(0,95, by=5))
  return(perdiff)
}

x <- as.vector(data$label)

result.ratio = mdply(unique(x), midshaft.ratio.function)


#Reshape into long format in order to plot 
result.ratio.long <- melt(result.ratio, variable.name="level", value.name="percent.difference")

result.ratio.long <- rbind(result.ratio.long[which(result.ratio.long$level == 30),], 
                           result.ratio.long[which(result.ratio.long$level == 35),],
                           result.ratio.long[which(result.ratio.long$level == 40),],
                           result.ratio.long[which(result.ratio.long$level == 45),],
                           result.ratio.long[which(result.ratio.long$level == 50),],
                           result.ratio.long[which(result.ratio.long$level == 55),],
                           result.ratio.long[which(result.ratio.long$level == 60),],
                           result.ratio.long[which(result.ratio.long$level == 65),],
                           result.ratio.long[which(result.ratio.long$level == 70),])



#Now the same function, but with the raw data in order to perform the statistical tests (this is just repeating all steps up to, but not including calculating percentages) 
midshaft.raw.ratio.function <- function(x)
{
  slicelength <- as.numeric(length(ratio[which(label == x)]))
  slice.intervals <- as.integer(seq(1,slicelength, by=(slicelength*.05)))
  slice.intervals <- slice.intervals + min(slice[which(label == x)])
  slicelength <- slicelength + (min(slice[which(label == x)])-1)
  slice.bind <- cbind(seq((min(slice[which(label == x)])), slicelength), (ratio[which(label == x)]))
  slice.bind <- rbind(matrix(nrow = (min(slice[which(label == x)])-1), ncol=2), slice.bind)
  slice.matrix <- as.matrix(slice.bind[slice.intervals, ])
  ratio.levels <- data.frame(rbind(slice.matrix[,2]))
  ratio.levels <- cbind(x, ratio.levels)
  colnames(ratio.levels) <- c("specimen", seq(0,95, by=5))
  return(ratio.levels)
}


raw.ratio.result = mdply(unique(x), midshaft.raw.ratio.function)
raw.result.ratio.long <- melt(raw.ratio.result, variable.name="level", value.name="raw.value")


#inverse of previous result.ratio.long to keep specimen names for the anova-- probably need to change for all 
raw.result.ratio.long <- raw.result.ratio.long[-c((which(raw.result.ratio.long$level == 0)), (which(raw.result.ratio.long$level == 5)),(which(raw.result.ratio.long$level == 10)), (which(raw.result.ratio.long$level == 15)),(which(raw.result.ratio.long$level == 20)), (which(raw.result.ratio.long$level == 25)),(which(raw.result.ratio.long$level == 75)),(which(raw.result.ratio.long$level == 80)),(which(raw.result.ratio.long$level == 85)),(which(raw.result.ratio.long$level == 90)),(which(raw.result.ratio.long$level == 95))),]


#Repeated measures ANOVA####
#Standard repeated measures anova (correcting for repeated measures from the same specimen)
m <- aov(terms(raw.result.ratio.long$raw.value ~ raw.result.ratio.long$level + (raw.result.ratio.long$specimen)))
m <- TukeyHSD(m)
midshaft.aov <- c('50-30','50-35','50-40','50-45', '55-50', '60-50', '65-50','70-50')
ratio.aov <- m$`raw.result.ratio.long$level`[midshaft.aov,]



#Paired T-test of all levels against midshaft
ratio.ttest <-as.data.frame(cbind( c(30,35,40,45,55,60, 65,70), c(t.test(raw.ratio.result$'50', raw.ratio.result$'30', paired=T)$p.value,
                                                                  t.test(raw.ratio.result$'50', raw.ratio.result$'35', paired=T)$p.value,
                                                                  t.test(raw.ratio.result$'50', raw.ratio.result$'40', paired=T)$p.value,
                                                                  t.test(raw.ratio.result$'50', raw.ratio.result$'45', paired=T)$p.value,
                                                                  t.test(raw.ratio.result$'50', raw.ratio.result$'55', paired=T)$p.value,
                                                                  t.test(raw.ratio.result$'50', raw.ratio.result$'60', paired=T)$p.value,
                                                                  t.test(raw.ratio.result$'50', raw.ratio.result$'65', paired=T)$p.value,
                                                                  t.test(raw.ratio.result$'50', raw.ratio.result$'70', paired=T)$p.value)))
colnames(ratio.ttest) <- c("level", "p-value")
#Bonferroni Correction to these p-values
ratio.ttest[,2] <- p.adjust(ratio.ttest[,2], method = "bonferroni", n = length(ratio.ttest[,2]))

#Compare Results of ANOVA and T-test:
ratio.pvalues <- cbind(ratio.aov[,-c(1:3)], ratio.ttest[,2])
colnames(ratio.pvalues) <- c("R.M. ANOVA", "Paired T-Test")
ratio.pvalues


#And the same significance tests on the logged values####
m <- aov(terms(log(raw.result.ratio.long$raw.value) ~ raw.result.ratio.long$level + (raw.result.ratio.long$specimen)))
m <- TukeyHSD(m)
midshaft.aov <- c('50-30','50-35','50-40','50-45', '55-50', '60-50', '65-50','70-50')
log.ratio.aov <- m$`raw.result.ratio.long$level`[midshaft.aov,]

#Paired T-test of all levels against midshaft
log.ratio.ttest <-as.data.frame(cbind( c(30,35,40,45,55,60, 65,70), c(t.test(log(log(raw.ratio.result$'50')), log(raw.ratio.result$'30'), paired=T)$p.value,
                                                                      t.test(log(raw.ratio.result$'50'), log(raw.ratio.result$'35'), paired=T)$p.value,
                                                                      t.test(log(raw.ratio.result$'50'), log(raw.ratio.result$'40'), paired=T)$p.value,
                                                                      t.test(log(raw.ratio.result$'50'), log(raw.ratio.result$'45'), paired=T)$p.value,
                                                                      t.test(log(raw.ratio.result$'50'), log(raw.ratio.result$'55'), paired=T)$p.value,
                                                                      t.test(log(raw.ratio.result$'50'), log(raw.ratio.result$'60'), paired=T)$p.value,
                                                                      t.test(log(raw.ratio.result$'50'), log(raw.ratio.result$'65'), paired=T)$p.value,
                                                                      t.test(log(raw.ratio.result$'50'), log(raw.ratio.result$'70'), paired=T)$p.value)))
colnames(log.ratio.ttest) <- c("level", "p-value")
#Bonferroni Correction to these p-values
log.ratio.ttest[,2] <- p.adjust(ratio.ttest[,2], method = "bonferroni", n = length(ratio.ttest[,2]))


#Compare Results of logged ANOVA and T-test:
log.ratio.pvalues <- cbind(log.ratio.aov[,-c(1:3)], log.ratio.ttest[,2])
colnames(log.ratio.pvalues) <- c("R.M. ANOVA", "Paired T-Test")
log.ratio.pvalues
```

####  P-values of Repeated measures Anova and Paired T-tests: J
```{r, echo=FALSE}
J.pvalues
```

####  P-values of Repeated measures Anova and Paired T-tests: Imax/Imin
```{r, echo=FALSE}
ratio.pvalues
```

*All t-test p-values have been corrected for multiple comparisons (Bonferoni).*
*Repeated measures ANOVA Tukey's poc hoc p-values were NOT corrected for multiple comparisons.*




